### 2018-07-12 paper/sphinxes.tex
WIP on Sphinxes

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates a header, this is a modification of that of 
    Sphinx~\cite[\S 3.2, \S 3.4]{Sphinx}.
  \item \(\WrapHeader\) is used to wrap a given single-use reply block given 
    the proper keys.
  \item \(\AttachPayload\) attaches a payload to the header, \ie makes it 
    sendable.
    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.
  \item \(\Process\) is the algorithm for processing incoming messages, the 
    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
    different interface.
\end{itemize}

@@

@@

The \(\CreateHeader\) algorithm is based on that of Sphinx~\cite[\S 
3.2]{Sphinx}.

>>>>

Sphinxes provides the following algorithms:
\begin{itemize}
  \item \(\CreateHeader\) creates an extendible header.
    It outputs a header with space left for a few layers and the needed keys to 
    add additional layers.

  \item \(\WrapHeader\) is used to wrap a given header using the proper keys.

  \item \(\AttachPayload\) attaches a payload to the header using the proper 
    keys.
    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.

  \item \(\Process\) is the algorithm for processing incoming messages, the 
    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
    different interface.
\end{itemize}

@@

\paragraph*{The \(\CreateHeader\) algorithm}

@@

This algorithm creates a header for \iac{POR}.
It takes as input a unique identifier \(I\in \bin^\kappa\) and a set of layers 
\(L = \{N_0, \dotsc, N_\nu\}\) such that \(\nu+1\leq r\).
